Monte Carlo Expectation Maximization for RNAseq

### 2015-06-17 slides/EM/em.Rnw
split plot

  mu_theta = mean(draws$theta)
  tau_theta = mean((draws$theta-mu_theta)^2)
  mu_psi = mean(draws$psi)
  tau_psi = mean((draws$psi-mu_psi)^2)
  keep$mu_theta[i] = mu_theta; keep$tau_theta[i] = tau_theta
  keep$mu_psi[i] = mu_psi; keep$tau_psi[i] = tau_psi
}
@

<<dependson=c('normal_hierarchical_mean_em','normal_hierarchical_mean_mcem'), echo=FALSE>>=
ggplot(melt(keep, id.var=c("iteration"), variable.name="parameter"),
       aes(iteration, value)) +
  geom_point() + 
  facet_wrap(~parameter, scales="free_y") +
  geom_hline(data=melt(truth, variable.name='parameter'), aes(yintercept=value))
@

>>>>

  mu_theta = mean(draws$theta)
  tau_theta = mean((draws$theta-mu_theta)^2)
  mu_psi = mean(draws$psi)
  tau_psi = mean((draws$psi-mu_psi)^2)
  keep$mu_theta[i] = mu_theta; keep$tau_theta[i] = tau_theta
  keep$mu_psi[i] = mu_psi; keep$tau_psi[i] = tau_psi
}
@
\end{frame}

\begin{frame}[fragile]
<<dependson=c('normal_hierarchical_mean_em','normal_hierarchical_mean_mcem'), echo=FALSE>>=
ggplot(melt(keep, id.var=c("iteration"), variable.name="parameter"),
       aes(iteration, value)) +
  geom_point() + 
  facet_wrap(~parameter, scales="free_y") +
  geom_hline(data=melt(truth, variable.name='parameter'), aes(yintercept=value))
@
